Linear Variation and an Optimization of Algorithms for Connected Components Labeling in a Binary Image

### 2016-04-19 paper/paper.tex
Add caption to normed pics, clarify total time measurement

So the benchmark charts show three levels of optimization applied to
DFS, SUF and SUF2:
just method name in legend refers to method applied to non-condensed image,
``+view'' means lazy memory-less condensation
and ``+2x2'' means that a temporary condensed image was constructed in memory.
For the latter case, the construction time was included into the overall measured
time of run.

@@

The test images were generated in the following manner. At first, 
for given density $d$, the first $4dNM$ pixels of
the $2N \times 2M$ image were filled with object values, while rest filled with background values.
Then all the pixels were permuted using \texttt{std::shuffle} function from \CXX standard library,
which is an implementation of Fisher-Yates Shuffle algorithm\cite{fisher:yates}.

@@

@@

Line charts with benchmarks of mentioned algorithms on different noise images
are shown on
\Cref{fig:overall:times}.

The extremely bigger CPU time for SUF and DTSUF methods on huge images could be
explained by significant increase in the number of cache-misses produced by
Union-Find. The charts prove effectiveness of the $2 \times 2$ condensation
optimization.

\begin{figure}
  \centering
  \includegraphics[height=0.45\textheight, keepaspectratio]{pics/overall.eps}
  \caption{Average CPU time per run on random images $1200 \times 1800$ px.}
  \label{fig:overall:times}
\end{figure}

\newcommand{\inputnorm}[1]{
  \begin{subfigure}[t]{0.45\linewidth}
    \centering
    \includegraphics[width=\textwidth,
                     keepaspectratio]{pics/normed_#1.eps}
    \caption{Some.}
    \label{fig:normed:#1}
  \end{subfigure}
}

\begin{figure}
  \centering
  \inputnorm{DFS}
  \inputnorm{SUF}
  \inputnorm{SUF2}
  \inputnorm{DTSUF}
  \label{fig:normed}
\end{figure}

>>>>

So the benchmark charts show three levels of optimization applied to DFS, SUF
and SUF2: just method name in legend refers to method applied to non-condensed
image, `` on 2x2 view'' means lazy memory-less condensation and `` on 2x2 copy''
means that a temporary condensed image was constructed in memory. For the latter
case, the construction time was included into the overall measured time of run.

@@

The test images were random images, generated in the following manner. At first,
for given density $d$, the first $4dNM$ pixels of the $2N \times 2M$ image were
filled with object values, while rest filled with background values. Then all
the pixels were permuted using \texttt{std::shuffle} function from \CXX standard
library, which is an implementation of Fisher-Yates Shuffle algorithm.

@@

It is worth noting again that for ``2x2 copy'' optimization, the apparent time
overhead of constructing the extra condensed image  was included into the total
run time, since we measured the total time between calling the CC counting
subroutine, supplied with only the original image, and returning back from
it.

@@

Line charts with benchmarks of mentioned algorithms on different noise images
are shown on \Cref{fig:overall}.

\begin{figure}
  \centering
  \includegraphics[height=0.45\textheight, keepaspectratio]{pics/overall.eps}
  \caption{Average CPU time per run on random images $1200 \times 1800$ px.}
  \label{fig:overall}
\end{figure}

\newcommand{\inputnorm}[2]{
  \begin{subfigure}[t]{0.45\linewidth}
    \centering
    \includegraphics[width=\textwidth,
                     keepaspectratio]{pics/normed_#1.eps}
    \caption{Speedup of #2}
    \label{fig:normed:#1}
  \end{subfigure}
}

\begin{figure}
  \centering
  \inputnorm{DFS}{DFS optimizations}
  \inputnorm{SUF}{SUF optimizations}
  \inputnorm{SUF2}{SUF2 optimizations}
  \inputnorm{DTSUF}{SUF optimizations, relative to DTSUF performance}
  \caption{Speedup/density charts}
  \label{fig:normed}
\end{figure}
